Spotify Data

### 2024-11-21 paper/paper.qmd
Changed Captions

```{r, fig.width=4, fig.height=2}
#| label: fig-tem-val
#| fig-cap: Relationship of Tempo and Valence in David's Songs
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: tbl-valence
#| tbl-cap: Summarise Statistics of Valence in David's Songs
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: tbl-tempo
#| tbl-cap: Summarise Statistics of Tempo in David's Songs
#| echo: false
#| warning: false
#| message: false

>>>>

```{r, fig.width=4, fig.height=2}
#| label: fig-tem-val
#| fig-cap: Relationship between Pace and Key in David's Songs
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: tbl-valence
#| tbl-cap: Summarise Statistics of Key in David's Songs
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: tbl-tempo
#| tbl-cap: Summarise Statistics of Pace in David's Songs
#| echo: false
#| warning: false
#| message: false
